Plots for Latent Hawkes Paper

### 2020-12-16 output_scripts/Paper_Plots.Rmd
add new fig4a and compete gist so all code in repo

@@

drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[1], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                          title_name=paste(plot.i,"->",plot.j),
                          title.cex = 2,
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])

>>>>

```
```{r fig4a-new-hist, fig.height=3.5,fig.width=8}
model_colors <- col_df %>% filter(method %in% c("C-HP",
                                                "C-DCHP",
                                                "C-MMHP"))

model_colors <- model_colors %>% pull(cols)

m1 <- sim_model3_stan_sim1_total %>%
  map( ~apply(.x$f, 2, mean)  ) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
         method = "C-HP")

m2 <- sim_model3_stan_sim2_total %>%
  map( ~apply(.x$f, 2, mean)  ) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
         method = "C-DCHP")

m3 <- sim_model3_stan_sim3_total %>%
  map( ~apply(.x$f, 2, mean)  ) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
         method = "C-MMHP")

rank_means <- bind_rows(m1,m2,m3)

# rank_means

true_values <- tibble(
  id = c("f1", "f2","f3","f4","f5"),
  values = c(0.1,0.2,0.4,0.7,0.9),
  val_names = c("   0.1","0.2","0.4","0.7","0.9")
)

rank_means %>% 
  left_join(true_values, by = c("node_id" = "id")) %>%
  ggplot(aes(value, fill = method)) + 
  geom_histogram() + 
  geom_vline(aes(xintercept = values), alpha = 0.6,
             linetype = "dashed") +
  ### add text here
  geom_text(aes(values, 18, label = val_names),
            size = 3, hjust = 1) +
  scale_fill_manual(values = model_colors) +
  facet_grid(cols = vars(node_id), rows = vars(method)) + 
  theme_bw() + theme(
    plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
    text = element_text(size = 12),
    axis.text.x=element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "", y = "")

@@

drawUniMMHPIntensityPaper(true.object,
                          simulation = fixStateTransition(test.mmhp),
                          yupper=y.ub[1], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2,
                          min.x=0, max.x=my.xlim,
                          title_name=paste(plot.i,"->",plot.j),
                          title.cex = 2,
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])
